Predicting instabilities of a tuneable ring laser with an iterative map model

### 2021-06-14 Papers/Journal/Metherall_JOSA_B.tex
TeX file including the cavity figure since you can only submit one TeX file

\begin{figure}[tbp]
	\centering
	\input{Cavity}
	\caption{Common cavity construction of a fibre ring laser~\cite{burgoyne2014, chung2017, lapre2019, shao2019}. The laser travels clockwise around the loop, with most of the pulse exiting the cavity through the optical coupler. CFBG, chirped fibre Bragg grating; OC, optical circulator; WDM, wavelength division multiplexer.}
	\label{fig:cavity}
\end{figure}

>>>>

\begin{figure}[tbp]
	\centering
	\begin{tikzpicture}
		% Two laser loops
		\draw [rounded corners=4mm] (0,0) rectangle ++(-1,4); % Pump
		\draw [fill=white, white] (0, -0.1) rectangle ++(-1.1,2); % Hide pump
		\draw [rounded corners=4mm] (0,0) rectangle ++(6,4); % Main

		% Isolator
		\filldraw[fill=white, draw=black] (1,-0.25) rectangle ++(1,0.5) node [midway, anchor=north, yshift=-6] {Isolator};
		\draw[-triangle 90] (1.9,0) -- (1.1,0);
		\draw[very thick] (1.9,0) -- (1.2,0);

		% Gain
		\draw (0.5,2.25) circle (0.5cm);
		\draw (0.5,2) circle (0.5cm) node [anchor=west,xshift=0.5cm,align=center] {Er-doped \\ gain fibre};
		\draw (0.5,1.75) circle (0.5cm);

		% Modulator and pump
		\filldraw[fill=white, draw=black] (3,-0.75) rectangle ++(2,1.5) node [midway] {Modulator};
		\filldraw[fill=white, draw=black] (-1.6,1.5) rectangle ++(1.2,1) node [midway] {Pump};

		% Coupler and output
		\draw[-stealth] (3,4) -- (3,5.5) node [pos=0.75,anchor=west,xshift=0.25cm] {Laser output};
		\draw[densely dashdotted] (2.5,3.5) -- (3.5,4.5) node [pos=1,anchor=north,yshift=-0.75cm,align=center] {Optical \\ coupler};

		% Circulators
		\filldraw[fill=white, draw=black] (6,2) circle (0.5cm) node [anchor=west,align=center,xshift=0.5cm] {OC};
		\draw[->,>=stealth] (6,2.325) arc (90:360:0.325cm);

		% \filldraw[fill=white, draw=black] (0,0) circle (0.5cm);
		% \draw[->,>=stealth] (0,0.325) arc (90:360:0.325cm);

		% \filldraw[fill=white, draw=black] (0,4) circle (0.5cm);
		% \draw[->,>=stealth] (0,4.325) arc (90:360:0.325cm);

		% WDMs
		\filldraw[fill=white, draw=black] (-0.15,3.8) rectangle ++(0.3,-0.6) node [midway, anchor=west, xshift=3] {WDM};
		% \filldraw[fill=white, draw=black] (-0.15,0.2) rectangle ++(0.3,0.6) node [midway, anchor=west, xshift=2] {WDM};

		% Arrows
		% \draw [->,>=stealth,domain=20:70,blue] plot ({0.675*cos(\x)}, {0.675*sin(\x)});
		% \draw [->,>=stealth,domain=110:160,red] plot ({0.675*cos(\x)}, {0.675*sin(\x)});
		\draw [->,>=stealth,domain=110:160,blue] plot ({6+0.675*cos(\x)}, {2+0.675*sin(\x)});
		\draw [->,>=stealth,domain=200:250,blue] plot ({6+0.675*cos(\x)}, {2+0.675*sin(\x)});
		% \draw [->,>=stealth,domain=200:250,red] plot ({0.675*cos(\x)}, {4+0.675*sin(\x)});
		% \draw [->,>=stealth,domain=290:340,blue] plot ({0.675*cos(\x)}, {4+0.675*sin(\x)});

		\draw [->,>=stealth,domain=270:360,blue] plot ({2.325+0.5*cos(\x)}, {4.675+0.5*sin(\x)});
		\draw [->,>=stealth,blue] (2.125, 4.675-0.5) -- (2.325+0.6, 4.675-0.5);

		% Grating
		\draw (5.5,2) -- (3.5,2) node [pos=0.5,anchor=south,yshift=0.25cm,xshift=-0.15cm] {CFBG};
		\foreach \i in {0,...,13}
			\draw (3.5 + \i*\i/100,1.75) -- (3.5 + \i*\i/100,2.25);

	\end{tikzpicture}
	\caption{Common cavity construction of a fibre ring laser~\cite{burgoyne2014, chung2017, lapre2019, shao2019}. The laser travels clockwise around the loop, with most of the pulse exiting the cavity through the optical coupler. CFBG, chirped fibre Bragg grating; OC, optical circulator; WDM, wavelength division multiplexer.}
	\label{fig:cavity}
\end{figure}
